\pagebreak
%% Introduction
\section{Introduction}

Wave generation solvers using Higher Order Spectral Method (HOS) have been validated and developed for several years (\cite{ducrozet2016}, \cite{ducrozet2007}, \cite{bonnefoy2011} and \cite{ducrozet2012}). HOS solves nonlinear wave propagation in open-sea (HOS-Ocean) and also in numerical wave tank (HOS-NWT) with low computation time comparing with other nonlinear wave solvers because the theory is based on pseudo-spectral method (\cite{HOSOcean} and \cite{HOSNWT}). Those HOS wave solvers are released as open-source codes, which anyone can develop, use and distribute under the terms of GNU General Public Licence (GPLv3).

Nonlinear irregular wave generation in computational fluids dynamic (CFD) solvers becomes important recently in naval fields to better estimate the loads on offshore structure. The conventional linear superposition methods imply a long computational time for wave generation and the simulation is made almost impossible without having enough computational power. And if the method is based on linear wave theory, there is also question on occurence of nonlinear phenomenon and the interaction between waves as the simulation goes. Therefore dedicated nonlinear wave solvers with high computational speed are needed.

\texttt{Grid2Grid} is developed as a wrapper program of HOS to generate wave fields from the results of HOS computation. \texttt{Grid2Grid} reconstructs wave fields of HOS with inverse fast Fourier transforms (FFTs) and uses a quick spline module, the nonlinear wave fields can be fastly reconstructed for arbitrary simulation time and space. The nonlinear wave simulation is then possible for a particular position and time where specific non linear phenomenon occur.

\texttt{Grid2Grid} compiles a shared library (\texttt{libGrid2Grid.so}) which can be used for communication with other progamming language using the \texttt{ISO\_C\_BINDING} rule. It compiles also a post processing program of HOS. 

