\input{docSetting.tex}

% Title
\title{Grid2Grid : HOS Wrapper Program }

\begin{document}

	%% Title Page
	\input{"titleSet.tex"}

	%% Table of Contents
	\tableofcontents	

	%% Introduction
	\input{introduction.tex}
	
	%% Program Structure
	\input{programStructure.tex}

		%% Surf2Vol
		\input{surf2vol.tex}    

		%% Vol2Vol
		\input{vol2vol.tex}    	

		%% Module Grid2Grid
		\input{modGrid2Grid.tex}
		
		%% Post Grid2Grid
		\input{postGrid2Grid.tex}	

	%% Installation
	\input{installation.tex}	

	%% Interface
	\input{interface.tex}
	
	%% Validation
	\input{validation.tex}
		
	%% Summary
	\pagebreak
	\section{Summary}
	
	HOS wrapper program called \texttt{Grid2Grid} is developed for the nonlinear wave simulation of numerical solvers. Most of data and functionality is encapsuled as a class to be easily used and maintained. \texttt{Grid2Grid} generates dynamic linked library as an independent package to be called and easily used in other languages. 
	
	The post processing of HOS is also possible by using \texttt{Grid2Grid}. Included post processing program is called \texttt{postGrid2Grid}. The usage is explained in Chapter \ref{chap:postGrid2Grid}.
	
	\texttt{Grid2Grid} is validated by using the code \texttt{foamStar} based on standard multiphase solver of OpenFOAM and also with an experiment. In the experiment, waves corresponding to 1000 year return period in Gulf of Mexico are generated. The wave elevation is measured at the wave breaking position expected by HOS wave theory and compared with the results of the simulation. Good agreement is shown between the measurement and the numerical solutions and the nonlinear wave phenomenon is observed both in experiment and in simulation. 
	
	In this document, the \texttt{Grid2Grid} program architecture, class and module structure, principle class data and functionality are explained to understand the feature of \texttt{Grid2Grid} and to be easily applied to numerical solvers. The interface examples with other programming languages are given as a source code and also in \texttt{Grid2Grid} package. 	
	
	%% Appendix modCommG2G.f90
	%	\input{appendixCommGrid2Grid.tex}	

	%% References
	\pagebreak
	\bibliography{reference}

	\bibliographystyle{apalike}

\end{document}
